A Database Management System for a Geospatially-Enabled Interactive Game

### 2018-10-28 paper/MSDS7330DBMSforGeospatiallyEnabledGame.tex
A bit more to Databse Schema section

>>>>

Player information, story segment information, and information about the five categories of tokens can be stored in their own tables. There will be a central table that links these various entities via a Game-ID. This in anticipation that we may want to tell two stories in the same cities. A list of geospatial points that correspond to viable latitudes and longitudes that can be used for any particular game will be stored separately from the list of geospatial points actually available to the player. This will allow us to update the list and properties of physical geospatial points without affecting existing games and applications. A diagram of the database schema can be found below in \autoref{ERD}.

\begin{figure}[H]
\centering
\includegraphics[width=2.7in]{imgs/MSDS7330_FinalProj_Prelim_ER2.png}
\caption{Entity Relationship Diagram of Game Database}
\label{ERD}
\end{figure}
